Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-05-16 ms.tex
I added some more details on the IRAF reduction of the HDS spectrum.

>>>>

\section{Subaru Analysis}

The host star \shStar\ has been characterized by both photometry and spectroscopy.
In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}
We decided to re-visit the high resolution spectrum from \citet{kawahara2013starspots} by downloading the raw data from the Subaru SMOKA database.

We follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/specana2014.10e.pdf}.
Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
We applied bad pixel masks and bias files to each CCD.
